---
title: "R Notebook"
output: html_notebook
---

DoOR dataset is only accessible in R. 

# load pacakges 
```{r}
library(dplyr)

# installed from https://github.com/ropensci/DoOR.data 
library(DoOR.data)
# installed from https://github.com/ropensci/DoOR.functions 
library(DoOR.functions)
loadData()
# say yes 
```

# general exploration 
```{r}
# this step is not necessary, but shows that all the relevant dataframes have the same set of odours, therefore no need to aggregate 
# Get the names of all objects in the environment
env_objects <- ls()

# Initialize an empty list to store dataframes with the relevant columns
dfs_with_columns <- list()

# Loop through all objects in the environment
for (obj_name in env_objects) {
  # Check if the object is a dataframe
  if (is.data.frame(get(obj_name))) {
    df <- get(obj_name)
    # Check if the dataframe contains the three columns of interest
    if (all(c("Class", "Name", "InChIKey") %in% colnames(df))) {
      # Select the relevant columns and add a new column with the dataframe name
      selected_df <- df[, c("Class", "Name", "InChIKey")]
      selected_df$df_name <- obj_name
      # Add the selected dataframe to the list
      dfs_with_columns[[length(dfs_with_columns) + 1]] <- selected_df
    }
  }
}

# Concatenate all selected dataframes vertically
final_df <- do.call(rbind, dfs_with_columns)

# Print the final concatenated dataframe
print(final_df)

```

```{r}
final_df %>% 
  plyr::count(c('Class','Name', 'InChIKey'))
```
So all the meta information mapping between class, name and InChIKey are in all the relevant dataframes. So we only need one. 


## receptors vs. glumeruli in adults? 
```{r}
door_mappings %>% 
  filter(adult) %>% 
  group_by(glomerulus) %>% 
  summarise(n_receptor_per_glom = n_distinct(receptor)) %>% 
  arrange(desc(n_receptor_per_glom))

```

```{r}
door_mappings %>% 
  filter(glomerulus == '') %>% 
  filter(adult)
```


## any mismatch between recording and meta receptors? 
```{r}
# are all the receptors with data in door_mappings? 
table(colnames(door_response_matrix) %in% door_mappings$receptor)
```

```{r}
# which ones have meta information but no experimental data? 
setdiff(door_mappings$receptor, colnames(door_response_matrix))
```

## chemical descriptor vs. name 
```{r}
ab2B %>% 
  group_by(Name) %>% 
  summarise(n_InChI_per_name = n_distinct(InChIKey)) %>% 
  arrange(desc(n_InChI_per_name))
```
So it seems like we don't really have a choice except for using the chemical descriptors and the receptors, instead of the chemical names and the glomeruli. 

# save the relevant data 
```{r}
write.csv(door_response_matrix, 'data/door_response_matrix.csv')
write.csv(door_mappings, 'data/door_receptor_mappings.csv')
```


